The internal format of a parameter's content \hyperlink{struct_c_o_n_f_i_g_b8cae13203b07fabaa40e407fa8dbdfb}{CONFIG::inhalt} is always a String (char Pointer).

The use and interpretation of parameters is controlled by a number of Flags in the \hyperlink{group__special__options__mask}{Special Options Mask} :\hypertarget{parameter_types_parameter_datatypes}{}\subsection{Parameter Data Types}\label{parameter_types_parameter_datatypes}
\begin{itemize}
\item \hyperlink{group__special__options__mask_g64c30a2865061d0c1074bc6ec91e3dcf}{CF\_\-STR} : Entry is String.  ({\bf Default}).\item \hyperlink{group__special__options__mask_gb33869d596619ad14675c053925a42e0}{CF\_\-INT} : Entry is Integer. \item \hyperlink{group__special__options__mask_geefdbef320cbd7179f1fb0ebe0fcf5ce}{CF\_\-REAL} : Entry is Float. \item \hyperlink{group__special__options__mask_g1d1f1d1b6eac6b5d9970102318ab2667}{CF\_\-FLAG} : \hyperlink{parameter_types_parameter_type_flag}{FLAG Parameter Type}\end{itemize}
\hypertarget{parameter_types_processing_instructions}{}\subsection{Special Processing Instructions}\label{parameter_types_processing_instructions}
Specific processing of a String Parameter's Value/Content in various CFLIB functions can be triggered by these Flags:

You can mark a parameter as Time {\bf or} Date. These parameters will be initialized with {\em now\/} or {\em today\/} by \hyperlink{group__cflib__core_ge593ff607f853bd5fc16a16bb6759314}{cfinit()} when \hyperlink{config_levels_parsing_level_priorities}{Parsing Level Priorities} are controlled by a \hyperlink{group__special__options__mask_g8d6cd1608fef5638efe964da63edf2dd}{CF\_\-SET\_\-PUT} Flag in the \hyperlink{group__special__options__mask}{Special Options Mask} or on call of \hyperlink{group__setting__saving_g6f133f88dc253a6a80d13eed4d123063}{cfputtime()}:

\begin{itemize}
\item \hyperlink{group__special__options__mask_g0fde537a92deb77f75b21c9e8d306509}{CF\_\-TIME} : Time string. \item \hyperlink{group__special__options__mask_g1c5b511a34d2c0db6631539ba81a4386}{CF\_\-DATE} : Date string. \end{itemize}


\begin{itemize}
\item \hyperlink{group__special__options__mask_g675b6f8440beecc09fec54d17e9c3ee9}{CF\_\-FINDFILE} : Entry is filename to be searched for in the path.  \hyperlink{group__utilities_g4e4e8f9a03b7f3598b5efd199b9a67c9}{FindFile()} will be used on initialization to search the file in the {\bf path} found in Environment Variable {\bf PATH}. You can specify an alternative search path for this functionality in another database parameter with Flag \hyperlink{group__special__options__mask_gb383c1436888ea6b410141f7c0b1f306}{CF\_\-PATH} set in the corresponding \hyperlink{config_initializer}{Configuration Initializer} entry. Depending on the Operating System a list of possible of {\bf extensions} of executables will be tried, if no extension is given with the filename:\begin{itemize}
\item Linux, Unix: \char`\"{}sh\char`\"{}, \char`\"{}pl\char`\"{}\item DOS,Windows, OS2: \char`\"{}exe\char`\"{}, \char`\"{}com\char`\"{}, \char`\"{}bat\char`\"{}, \char`\"{}cmd\char`\"{}\item TOS, MinT: \char`\"{}ttp\char`\"{}, \char`\"{}tos\char`\"{}, \char`\"{}prg\char`\"{}, \char`\"{}app\char`\"{}, \char`\"{}gtp\char`\"{}\end{itemize}
\end{itemize}


\begin{itemize}
\item \hyperlink{group__special__options__mask_gff1b2e25aa9a89a55c1784018e24aa75}{CF\_\-EXPHOME} : Expand Home Directory.  See \hyperlink{group__advanced__features_gb6f874ac347d273dc45ad011808fe703}{cfhomexp()}. \hyperlink{config_files}{Configuration Files} will have home directory expanded by default\end{itemize}
\hypertarget{parameter_types_handling_instructions}{}\subsection{Special Handling Instructions}\label{parameter_types_handling_instructions}
A parameter can be marked as a {\bf \char`\"{}volatile\char`\"{}} entry that is not saved by \hyperlink{group__setting__saving_g046d8a68eae35b987eacca04a9a06cca}{cfsave()}:

\begin{itemize}
\item \hyperlink{group__special__options__mask_gd76153c65f68cc0ee5c1a04c8c3e80bf}{CF\_\-NOSAVE} : Don't include in savefile / mark entry. \end{itemize}
\hypertarget{parameter_types_cflib_parameters}{}\subsection{CFLIB Parameters}\label{parameter_types_cflib_parameters}
Some String Parameters in the configuration database are used by the library itself and are marked by one of the following Flags:

\begin{itemize}
\item \hyperlink{group__special__options__mask_g071c29b5177f2df2400712ce8daae9b0}{CF\_\-PRGNAME} : Running Program's Name from commandline.  This parameter {\bf always} exists as the {\bf first} entry in a configuration database successfully initialized by \hyperlink{group__cflib__core_ge593ff607f853bd5fc16a16bb6759314}{cfinit()}. The default parameter name used if there was no corresponding entry in the Initializer is {\bf \char`\"{}CF\_\-PRGNAME\char`\"{}}.\item \hyperlink{group__special__options__mask_gfeeb63d4d8c498bec4a237ad8b94f02f}{CF\_\-SETFILE} : Entry is Private Configuration File.  See \hyperlink{config_files}{Configuration Files}\item \hyperlink{group__special__options__mask_gbb03ea68e07e388da2c1337a1582c72e}{CF\_\-SYS\_\-SETFILE} : Entry is System Configuration File.  See \hyperlink{config_files}{Configuration Files}\item \hyperlink{group__special__options__mask_g603f0467f101b71f5f869381429ffef4}{CF\_\-SECTION} : Section in Configuration File.  See \hyperlink{config_files}{Configuration Files}\item \hyperlink{group__special__options__mask_gb383c1436888ea6b410141f7c0b1f306}{CF\_\-PATH} : Search Path (for FindFile feature).  See \hyperlink{group__special__options__mask_g675b6f8440beecc09fec54d17e9c3ee9}{CF\_\-FINDFILE} and \hyperlink{group__utilities_g4e4e8f9a03b7f3598b5efd199b9a67c9}{FindFile()}\item \hyperlink{group__special__options__mask_gc30981201d7455071cef38a0133b9228}{CF\_\-USAGE} : Usage Message format string.  See \hyperlink{group__retrieval_ge272c1881db940e56c8cc364df730271}{cfgetusg()}\end{itemize}


Optional Parameters for fine tuning CFLIB behavior without Special Option Flag, characterized by Parameter Name:

\begin{itemize}
\item {\bf \char`\"{}CF\_\-DUMPVERB\char`\"{}} - Non-Default Verbosity Mode for \hyperlink{group__advanced__features_gecfc8ee37366e1b36cb5aac0cc41ebdc}{cfdump()}\end{itemize}
\hypertarget{parameter_types_parameter_type_flag}{}\subsection{FLAG Parameter Type}\label{parameter_types_parameter_type_flag}
The entry is treated like a boolean variable and the string content set from any of the \hyperlink{config_levels}{Configuration Parsing Levels and Source/Origin Options} except the default setting is interpreted as follows:

\begin{itemize}
\item \hyperlink{group__cflib__core_g7010abac2c80c121772da4d9c03332ee}{CF\_\-FLAG\_\-OFF} : String Content is:\begin{itemize}
\item beginning with a {\tt '-'} \item {\tt \char`\"{}OFF\char`\"{}} or {\tt \char`\"{}off\char`\"{}} \item {\tt \char`\"{}FALSE\char`\"{}} or {\tt \char`\"{}false\char`\"{}} \end{itemize}
\item \hyperlink{group__cflib__core_g355c714f2912ac336b8b03468c978d8c}{CF\_\-FLAG\_\-ON} : any other case\end{itemize}
\begin{Desc}
\item[Example:]\begin{itemize}
\item Initializer entry: \{ \char`\"{}extended\_\-message\char`\"{}, CF\_\-FLAG\_\-OFF, 'x', CF\_\-FLAG, \}\item Commandline: myprog -x-\item Configuration file: extended\_\-message = OFF \end{itemize}
\end{Desc}
